### 2017-09-06 Documents/bootcamp_topic_intro.tex
Fixed Typos

\section*{\href{https://atom.io/}{Atom}}
\begin{itemize}
\item A versatile, text editor. Must have tool for serious work.
\item We will use it to open files, look at them, learn some markdown.
\item Lets install it
\begin{itemize}
\item Put red sticker on your laptop
\item Google ``atom download'' or borrow a USB drive
\item Download or copy installer to your computer
\item Run installer
\item Start Atom
\item Replace red sticker with green when Atom opens
\end{itemize}
\item Go and open new file
\item type my first file, then comma, then birth year, then comma, high school graduation year, then comma, college graduation year (or expected graduation year). For me it is like this\\
    \\
{\tt my first file, 1978, 1996, 2001} 
\item Save as: \verb|my-first-file.csv| in your \verb|Data_Bootcamp| file.
\item \textbf{Pro-tip: naming convention and file type is important in this course}
\end{itemize}

\section*{\href{https://github.com}{GitHub}}
\begin{itemize}
\item What I will use it for\ldots
\begin{itemize}
\item Source of ALL course materials
\item Place for you to grab materials on the fly. Save files by cut and paste, clever save as, or "Raw" (ask about this)
\end{itemize}
\item You need to create an account and email me your username
\item What you will use it for\ldots
\begin{itemize}
\item Post your homework and projects; I will ``pull'' them from there.
\item Long run: Think of this like an artists portfolio. Here you can post your code and projects and show potential employers, family, friends what you have done.
\end{itemize}
\item Now lets use it
\begin{itemize}
\item Create a new repository and name it {\tt my-first-repository},
\item place the \verb|my-first-file.csv| file you created in it,
\item Great job! Next class, I'm going to try and ``pull'' the file and then report some statistics about the class to you.
\end{itemize}
\end{itemize}

>>>>

\section*{\href{https://atom.io/}{Atom}}
\begin{itemize}
\item A versatile, text editor. Must have tool for serious work.
\item We will use it to open files, look at them, learn some markdown.
\item Lets install it
\begin{itemize}
\item Put red sticker on your laptop
\item Google ``atom download'' or borrow a USB drive
\item Download or copy installer to your computer
\item Run installer
\item Start Atom
\item Replace red sticker with green when Atom opens
\end{itemize}
\item Go and open new file
\item type ``my first file'', then comma, then birth year, then comma, high school graduation year, then comma, college graduation year (or expected graduation year). For me it looks like this\\
    \\
{\tt my first file, 1978, 1996, 2001} 
\item Save as: \verb|my-first-file.csv| in your \verb|Data_Bootcamp| file.
\item \textbf{Pro-tip: naming convention and file type is important in this course}
\end{itemize}

\section*{\href{https://github.com}{GitHub}}
\begin{itemize}
\item What I will use it for\ldots
\begin{itemize}
\item Source of ALL course materials
\item Place for you to grab materials on the fly. Save files by cut and paste, clever save as, or "Raw" (ask about this)
\end{itemize}
\item You need to create an account and email me your username
\item What you will use it for\ldots
\begin{itemize}
\item Post your homework and projects; I will ``pull'' them from there.
\item Long run: Think of this like an artists portfolio. Here you can post your code and projects and show potential employers, family, friends what you have done.
\end{itemize}
\item Now lets use it
\begin{itemize}
\item Create a new repository and name it {\tt my-first-repository},
\item place the \verb|my-first-file.csv| file you created in it,
\item Great job! \\
Next class, I'm going to try and ``pull'' the file and then report some statistics about the class to you.
\end{itemize}
\end{itemize}
